### 2017-04-01 paper/evaluation.tex
fix macros at evaluation

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused given that only \Fix{\%}
      of projects supports parallel execution of test suites.}
  \end{minipage}
}
\end{center}

>>>>

\begin{center}
\fbox{
  \begin{minipage}{8cm}
      \textit{Answering \numRQC{}:}~\emph{Overall, results indicate
      that parallelism features are underused given that only
	  \percentParallel{}
      of projects supports parallel execution of test suites.}
  \end{minipage}
}
\end{center}
